The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-07 paper.tex
update

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.

@@

\subsection{Gamma-ray and microwave emission}

  In this section, we compare the simulated gamma-ray and microwave\
  spectra based on the leptonic AGN jet model with the\
  observed spectra of the Fermi bubbles and the microwave haze.\
  The gamma-rays originate from the inverse Compton scattering of ISRF by CRe.\
  The CRe spectrum follows a power-law distribution\
  with a spectral index $p=2.4$ and ranges from\
  $m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
  where $m_{\text{e}}c^2$ is the rest mass energy of an electron.

  The emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
  each computational cell in our simulations\
  using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
  to handle the ultra-relativistic CRe:

@@

\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
in the energy bin $76.8-153.6$ GeV.\

One can see that the symmetric of the \textit{Fermi} bubbles can also be reproduced by tilted jets.\

  The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
  within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
  and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.

@@

  \Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
  and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.

  For a given longitude and latitude range, the simulated spectra are\
  computed by projecting the gamma-ray/microwave emissivities as a\
  function of energy along finely sampled lines of sight\
  (with resolutions of 0.5 degrees), and then we average the spectra\
  over all the sight lines within the region.

  Indeed, we find that the simulated gamma-ray\
  spectra for all latitudes exhibit a spectral cutoff at\
  similar energies 400--500 GeV, consistent with\
  the observed cutoff energy.

@@

>>>>

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight with resolutions of 0.5 degrees\
  from the solar position at $(x,y,z)=(8,0,0)$ kpc across the sky.

@@

\subsection{Gamma-ray and microwave spectra: constraint on the CRe spectral index}

In this section, we give the constraint on the CRe spectral index by\
comparing the simulated gamma-ray and microwave spectra\
with the observed spectra of the Fermi bubbles \citet{Ackermann2014}\
and the microwave haze \citep{Dobler_2008}, respectively.\

The simulated gamma-ray and microwave spectra is based on the\
IC scattering and synchrotron from CRe, in which\
the CRe spectrum follows a power-law distribution ranging from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV),\
where $m_{\text{e}}c^2$ is the rest mass energy of an electron.

%The microwave haze at 23 GHz was first detected by the \textit{WMAP} \citep{Dobler_2008}\
%within the region $|b|<30^{\circ}$ above and below the Galactic plane,\
%and later confirmed by the Planck Collaboration IX \citep{PlanckCollaborationIX2013}.

The IC emissivity of the upscattered photons at the energy $\epsilon_{1}$ is computed for\
each computational cell in our simulations\
using the Klein-Nishina IC cross-section \citep{Jones1968,BLUMENTHAL1970}\
to handle the scattering between ultra-relativistic CRe and ISRF:

@@

@@

For a given longitude and latitude range, the simulated spectra are\
computed by projecting emissivities\
as we project X-ray emissivities in Section \ref{X-ray},\
and then we average the spectra over all the sight lines within the region on sky.

\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.
The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\

We find that the simulated gamma-ray\
spectra for all latitudes exhibit a spectral cutoff at\
similar energies 400--500 GeV, consistent with\
the observed cutoff energy.

@@

  We display the morphology of the \textit{Fermi} bubbles\
  that emit gamma-rays from the inverse Compton scattering of ISRF by CRe.

\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
can also be realized by tilted jets as the eROSITA bubbles.\
